### 2019-03-16 README.Rmd
Fix typos

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the Convention on International Trade in Endangered Species).

@@

The back-end database, [MonetDB](https://monetdb.org) is very fast and powerful, making such
analyses quite snappy even on such large data and normal desktops and laptops. Here's the
timing of the above query, which procecsses over 20 million records, on an ordinary laptop:

>>>>

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the Convention on International Trade in Endangered Species.

@@

The back-end database, [MonetDB](https://monetdb.org) is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which procecses over 20 million records, on an ordinary laptop:
